TGI-spinal-power

### 2022-05-09 analysis/tgispine_lme_power.Rmd
trying and failing to run power analysis, time to rest

# Run power analysis - to do this use the simplest model (model.cold)
# First, Create a model with more data points per variable, to extract more power
```{r}
# First, let's try to add 30 observations per variable combination, which would mean N = 30
model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
summary(model.coldN)
# check that number of data points per variable does = 30
dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.coldN))
print(dat_model)
```

# Run power analysis!
````{r, results = 'hide'}
# extract fixed effects from the model - take the lowest effect size from the model
tgi_effect <- fixef(model.coldN)["manipulationTGI"]
cond_effect <- fixef(model.coldN)["conditionwithin"]
cold_loc_effect <- fixef(model.coldN)["cold_locationprox_caud"]
# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
# change the effect size to effect size of interest
fixef(model.coldN)["cold_locationprox_caud"] <- cold_loc_effect

# then run power analysis
pwr.cold <- powerSim(model.coldN)
print(pwr.cold)
```

Now to run a power curve on the data to find out the optimal number of participants needed for the effect of interest
```{r}
# can run a power curve to determine the point of trade off between N observations and power
pc.cold <- powerCurve(model.coldN, within='manipulation+condition+cold_location', 
                      breaks= seq(1, 30, by = 3))
print(pc.cold)
```

>>>>

Cold model power analysis
# Run power analyses!!
# Cold first, then warm
# Create a model with more data points per variable, to extract more power
```{r}
# First, let's try to add 30 observations per variable combination, which would mean N = 30
model.cold.ex <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
summary(model.cold.ex)
# check that number of data points per variable does = 30
dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.cold.ex))
print(dat_model)

# extract relevant effect sizes
tgi_effect <- fixef(model.cold.ex)["manipulationTGI"]
cond_effect <- fixef(model.cold.ex)["conditionwithin"]
cold_loc_effect <- fixef(model.cold.ex)["cold_locationprox_caud"]

# power analysis - using smallest effect size
fixef(model.cold.ex)["manipulationTGI"] <- cold_loc_effect
pwr.warm <- powerSim(model.warmN)
print(pwr.warm)

# power curve
# can run a power curve to determine the point of trade off between N observations and power
pc.cold <- powerCurve(model.cold.ex, within='manipulation+condition+cold_location', 
                      breaks= seq(1, 30, by = 3))
print(pc.cold)
```
